\bf Supplementary Material to\\ ``Nonparametric Block Bootstrap Kolmogorov-Smirnov Goodness-of-Fit Test''

### 2025-10-12 manuscript/manuscript.tex
minor

Theoretically, $K_n(x)$ and the simpler plug--in correction
$C_n(x)=\sqrt{n}\{F_n(x)-F(x;\hat\theta_n)\}$ are asymptotically
equivalent when the series is independent or exhibits only
short--memory dependence.  The joint process of $(F_n,\hat\theta_n)$
converges to a mean--zero Gaussian limit whose long--run covariance
aggregates auto--covariances across lags.  When the circular block
bootstrap reproduces this long--run covariance, the conditional bias of
the plug--in statistic is of smaller order $O_p(l/n)$, where $l$ is the
block length.  The expectation centering in $K_n(x)$ removes this minor
bias exactly but does not alter the first--order limit.  Consequently,
both corrections yield the same asymptotic distribution, and differences
appear only through higher--order terms that vanish as the sample size
increases.

To evaluate the finite--sample impact, we compared the two corrections
through additional simulations; see results in Section~1 in the
Supplement.  Across all sample sizes and dependence
levels considered, the empirical sizes and powers were nearly identical.
This finding supports the theoretical argument that the circular block
bootstrap already captures the leading effects of serial correlation,
leaving little residual bias for the expectation centering to remove.
The comparable results of $K_n(x)$ and $C_n(x)$ suggest that the choice
between them is largely immaterial in practice.  We therefore retain
$K_n(x)$ for theoretical completeness and consistency of presentation,
while acknowledging that either correction performs similarly in finite
samples.

@@

The KS test remains a crucial tool for researchers across diverse fields,
enabling critical assessments of population distributions. We introduced a
NPBB variant of the KS test tailored for data with
serial dependencies, which eliminates the need for explicit modeling serial
dependence in addition to parameter specification within the hypothesized
distribution. Our simulations have demonstrated that, given
sufficiently large samples of time series data and moderate serial dependencies,
the test maintains its size under the null hypothesis and have considerable
power in detecting deviations from the hypothesized marginal distribution. The
method's performance improves as the strength of temporal dependence decreases
or the sample size increases. For moderate serial dependence levels in practice,
the test can be recommended for sample size~$n = 400$ or higher.
Overall, the test provides an analog of the bias-corrected NPB KS test of
\citet{babu2004goodness} in the context of stationary time
series with unspecified serial dependence. Compared to the SPB method
of \citet{zeimbekakis2024misuses}, which requires a working dependence model, it
is reliable with no need to worry about whether the working dependence
model approximates the true dependence model. We note that while the
expectation centering in our paper removes a minor bias term, it is identical
in asymptotic performance to \citet{babu2004goodness}'s correction under 
short--range dependence.

@@

Several promising directions for further research emerge from
this study. Firstly, while we used circular block bootstrap, many
other bootstrap variants for serially dependent data, such as the
stationary bootstrap \citep{politis1994stationary} and the dependent wild
bootstrap \citep{shao2010dependent}, could be evaluated under our
correction framework. Secondly, analogous methodologies could be
developed for other goodness-of-fit tests based on empirical
distributions, including the Anderson---Darling and Cramér--von
Mises tests, which are known to outperform the KS test in certain scenarios
\citep{stephens2017tests}. Applying block bootstrap bias correction to
these tests may be particularly beneficial in contexts like extreme
value modeling, where serial dependence is common. Third, it would be
intriguing to extend the proposed NPBB
one-sample KS test to a two-sample setting, allowing for comparison of
marginal distributions without specifying serial dependencies in
either sample. Finally, a rigorous theoretical justification of the
NPBB procedure, including precise conditions for the asymptotic
behavior of the test statistic and the consistency of the bootstrap
approximation, would offer valuable practical insights into the
scenarios where the NPBB approach is expected to perform optimally.
In particular, while the
correction term is designed to calibrate the null distribution of the
test statistic, studying its behavior under alternatives, including
contiguous alternatives, would further inform the power properties of
the method and remains an interesting direction for future research.

@@

>>>>

Theoretically, $K_n(x)$ and the simpler correction $C_n(x)$ are
asymptotically equivalent when the series is independent or exhibits
only short-memory dependence.  The joint process of
$(F_n,\hat\theta_n)$
converges to a mean-zero Gaussian limit whose long-run covariance
aggregates autocovariances across lags.  When the circular block
bootstrap reproduces this long-run covariance, the conditional bias of
$C_n$ is of smaller order $O_p(l/n)$, where $l$ is the
block length.  The expectation centering in $K_n(x)$ removes this minor
bias exactly but does not alter the first-order limit.  Consequently,
both corrections yield the same asymptotic distribution, and differences
appear only through higher-order terms that vanish as the sample size
increases.

To evaluate the finite sample impact, we compared the two corrections
through additional simulations; see results in Section~1 in the
Supplement.  Across all sample sizes and dependence
levels considered, the empirical sizes and powers were nearly identical.
This finding supports the theoretical argument that the circular block
bootstrap already captures the leading effects of serial correlation,
leaving little residual bias for the expectation centering to remove.
The comparable results of $K_n(x)$ and $C_n(x)$ suggest that the choice
between them is largely immaterial in practice.  We therefore retain
$K_n(x)$ for theoretical completeness and consistency of presentation,
while acknowledging that either correction performs similarly in finite
samples.

@@

The KS test remains a crucial tool for researchers across diverse fields,
enabling critical assessments of population distributions. We introduced a
NPBB variant of the KS test tailored for data with
serial dependencies, which eliminates the need for explicit modeling serial
dependence in addition to parameter specification within the hypothesized
distribution. Our simulations have demonstrated that, given
sufficiently large samples of time series data and moderate serial dependencies,
the test maintains its size under the null hypothesis and have considerable
power in detecting deviations from the hypothesized marginal distribution. The
method's performance improves as the strength of temporal dependence decreases
or the sample size increases. For moderate serial dependence levels in practice,
the test can be recommended for sample size~$n = 400$ or higher.
Overall, the test provides an analog of the bias-corrected NPB KS test of
\citet{babu2004goodness} in the context of stationary time
series with unspecified serial dependence. Compared to the SPB method
of \citet{zeimbekakis2024misuses}, which requires a working dependence model, it
is reliable with no need to worry about whether the working dependence
model approximates the true dependence model. We note that while the
expectation centering in our paper removes a minor bias term, it is identical
in asymptotic performance to \citet{babu2004goodness}'s correction under 
short-range dependence.

@@

Several promising directions for further research emerge from
this study. Firstly, while we used circular block bootstrap, many
other bootstrap variants for serially dependent data, such as the
stationary bootstrap \citep{politis1994stationary} and the dependent wild
bootstrap \citep{shao2010dependent}, could be evaluated under our
correction framework. Secondly, analogous methodologies could be
developed for other goodness-of-fit tests based on empirical
distributions, including the Anderson--Darling and Cramér--von
Mises tests, which are known to outperform the KS test in certain scenarios
\citep{stephens2017tests}. Applying block bootstrap bias correction to
these tests may be particularly beneficial in contexts like extreme
value modeling, where serial dependence is common. Third, it would be
intriguing to extend the proposed NPBB
one-sample KS test to a two-sample setting, allowing for comparison of
marginal distributions without specifying serial dependencies in
either sample. Finally, a rigorous theoretical justification of the
NPBB procedure, including precise conditions for the asymptotic
behavior of the test statistic and the consistency of the bootstrap
approximation, would offer valuable practical insights into the
scenarios where the NPBB approach is expected to perform optimally.
In particular, while the
correction term is designed to calibrate the null distribution of the
test statistic, studying its behavior under alternatives, including
contiguous alternatives, would further inform the power properties of
the method and remains an interesting direction for future research.

@@

\item[Additional simulation results:] Simulation studies on compariong
of two bias corrections and block size selection are reported in an
online pdf Supplement.

### 2025-10-12 manuscript/reply2.tex
minor

\textbf{Response to Comment on the Bias Correction Term.}

@@

A newly added paragraph clarifies that two bias corrections$C_n$ and
$K_n$ are asymptotically equivalent under independence and
short--memory dependence.  The preference for $K_n(x)$ arises from
theoretical considerations: under serial dependence, the bootstrap
analogue of $C_n(x)$ can exhibit a small $O_p(l/n)$ conditional bias
due to cross--lag covariances between $F_n(x)$ and $\hat\theta_n$,
where $l$ is the block length.  The expectation centering in $K_n(x)$
removes this bias without changing the first--order limit, yielding a
cleaner asymptotic argument.

>>>>

@@

A newly added paragraph clarifies that two bias corrections $C_n$ and
$K_n$ are asymptotically equivalent under independence and
short--memory dependence.  The preference for $K_n(x)$ arises from
theoretical considerations: under serial dependence, the bootstrap
analogue of $C_n(x)$ can exhibit a small $O_p(l/n)$ conditional bias
due to cross--lag covariances between $F_n(x)$ and $\hat\theta_n$,
where $l$ is the block length.  The expectation centering in $K_n(x)$
removes this bias without changing the first--order limit, yielding a
cleaner asymptotic argument.

### 2025-10-12 manuscript/supplement.tex
minor

A heuristic justification for the $K_n(x)$ bias correction term was
provided in the main manuscript. It may also help to demonstrate
empirically that this the block bootstrap KS test with the $K_n$ bias
correction holds its size at least as well as the block boostrap KS
test with the \citet{babu2004goodness} bias correction and is at
least as powerful. For this reason, we conducted a simulation study
with parameter settings identical to the main study in the paper
except for the choice of bias correction.

@@

Based on Figures~\ref{fig:qq_n_C_n, fig:qq_g_C_n, fig:rr_C_n}, 
the empirical performance in both size and power analysis is very similar under 
either choice of bias correction 
term. This suggests that the circular block bootstrap already corrects for
much of the temporal dependence, and that the choice of centering
has a very small effect on residual bias. Using $C_n(x)$ has the advantage
of requiring slightly less computation, but we 
still recommend $K_n(x)$ for its theoretical qualities, but acknowledge that
performance may be indistinguishable in practical application, especially
with large sample size and dependence that decays rapidly.

@@

We evaluated the size and power performance of the NPBB test under automatic
block length selection. The size performance is shown
in Figures~\ref{fig:alt_qq_n} and \ref{fig:alt_qq_g}, which display Q-Q plots
of the $p$-values under the null for Normal and Gamma margins, respectively.
Recall from the Q-Q plots in the main paper that the cubic root 
setting holds its size quite well with small $n$ for $|\tau| \leq 0.25$,
whereas achieving nominal size for $|\tau| \geq 0.5$ require
$n > 200$, and for $|\tau| \geq 0.75$ require $n > 800$. The automatic
selection shows similar limitations for $|\tau| > 0.5$, where it does
not hold its size. Moreover, deviations from the diagonal line appear
larger for negative $\tau$, likely due to the high proportion of
occurrence of overly large block sizes. For example, while the cubic
root setting held its size well at $\tau = -0.25$ with small~$n$, the
automatic selection does not. At the same time, under $\tau = 0$ or
$\tau = 0.25$, the method with block size selected by
\citep{politis2004automatic} maintains reasonable size for moderately
positively dependent series.

Figure~\ref{fig:alt_rr} shows the power results under automatic selection.
When compared to the power curve in the main paper, the two settings exhibit 
similar power
for $|\tau| \leq 0.5$, with the automatic selection sometimes yielding higher
rejection rates, particularly for smaller negatively dependent samples.
Overall, while the automatic selection from \citep{politis2004automatic}
performs reasonably well in certain settings, we recommend caution when using
it under negative~$\tau$ and smaller sample sizes, where maintaining nominal
size may be more difficult. In such cases, it may be sensible to apply a more
restrictive rule when setting the final block size---for example, using
$\min \{\sqrt{n}, \hat{l}\}$.

>>>>

A heuristic justification for the $K_n(x)$ bias correction term was
provided in the main manuscript. It may also help to demonstrate
empirically that this the block bootstrap KS test with the $K_n$ bias
correction holds its size at least as well as the block bootstrap KS
test with the bias correction $C_n$ in \citet{babu2004goodness} and is
at least as powerful. For this reason, we conducted a simulation study
with parameter settings identical to the main study in the paper
except for the choice of bias correction.

@@

Based on Figures~\ref{fig:qq_n_C_n}--\ref{fig:rr_C_n}, 
the empirical performance in both size and power analysis is very similar under 
either choice of bias correction 
term. This suggests that the circular block bootstrap already corrects for
much of the temporal dependence, and that the choice of centering
has a very small effect on residual bias. Using $C_n(x)$ has the advantage
of requiring slightly less computation, but we 
still recommend $K_n(x)$ for its theoretical qualities, but acknowledge that
performance may be indistinguishable in practical application, especially
with large sample size and dependence that decays rapidly.

@@

We evaluated the size and power performance of the NPBB test under automatic
block length selection. The size performance is shown
in Figures~\ref{fig:alt_qq_n} and \ref{fig:alt_qq_g}, which display Q-Q plots
of the $p$-values under the null for Normal and Gamma margins, respectively.
Recall from the Q-Q plots in the main paper that the cubic root 
setting holds its size quite well with small $n$ for $|\tau| \leq 0.25$,
whereas achieving nominal size for $|\tau| \geq 0.5$ require
$n > 200$, and for $|\tau| \geq 0.75$ require $n > 800$. The automatic
selection shows similar limitations for $|\tau| > 0.5$, where it does
not hold its size. Moreover, deviations from the diagonal line appear
larger for negative $\tau$, likely due to the high proportion of
occurrence of overly large block sizes. For example, while the cubic
root setting held its size well at $\tau = -0.25$ with small~$n$, the
automatic selection does not. At the same time, under $\tau = 0$ or
$\tau = 0.25$, the method with block size selected by
\citet{politis2004automatic} maintains reasonable size for moderately
positively dependent series.

Figure~\ref{fig:alt_rr} shows the power results under automatic selection.
When compared to the power curve in the main paper, the two settings exhibit 
similar power
for $|\tau| \leq 0.5$, with the automatic selection sometimes yielding higher
rejection rates, particularly for smaller negatively dependent samples.
Overall, while the automatic selection from \citet{politis2004automatic}
performs reasonably well in certain settings, we recommend caution when using
it under negative~$\tau$ and smaller sample sizes, where maintaining nominal
size may be more difficult. In such cases, it may be sensible to apply a more
restrictive rule when setting the final block size---for example, using
$\min \{\sqrt{n}, \hat{l}\}$.
